Using cosmic variance to constrain the dark matter halo mass of Lyman-alpha emitting galaxies at $z$=3.1

### 2013-05-31 paper/ms.tex
minor updates

In this section we consider two additional constraints on the models
we accept as succesul. First by taking models with the
highest possible number of mock surveys consistent with
observations. Second by including additional observational constraints
on the occupation fraction for high redshift LAEs.

@@

\section{Results for the Angular Correlation Function}

we calculate the angular correlation function
(ACF) for all the models having the $15$ mock surveys consistent with
observations. We perform this calculation as a sanity check and
potential additional constraint. The ACF is computed only the densest
subfield in all the 15 mock surveys corresponding to the SSA22
region. These results are compared against the observations reported
by \citep{Hayashino2004} which were also performed on the densest
field of SSA22.

>>>>

In this section we consider three additional constraints on the models
we accept as succesul. First by taking models with the
highest possible number of mock surveys consistent with
observations. Second by including additional observational constraints
on the occupation fraction for high redshift LAEs. Third by comparing
the angular correlation function against observational constraints by
\cite{Hayashino2004}.

@@

\subsection{Consitency with the Angular Correlation Function}

The measurementens presented in \citep{Yamada2012} do not present a
new measurement of the angular correlation function (ACF). However
\citep{Hayashino2004} performed such calculation on the LAEs observed
inthe densest field of SSA22.

we calculate the angular correlation function
(ACF) for all the models having the $15$ mock surveys consistent with
observations. We perform this calculation as a sanity check and
potential additional constraint. The ACF is computed only the densest
subfield in all the 15 mock surveys corresponding to the SSA22
region.
